gtsummary

### 2020-12-09 rmarkdown-gtsummary.Rmd
in progress

```{r}
trial %>%
  imap_dfr(
    ~tibble(
      colname = .y, 
      label = attr(.x, "label"), 
      class = class(.x), 
      values = trial %>% select(.y) %>% distinct() %>% 
        arrange(!!rlang::sym(.y)) %>% slice(1:4) %>% pull(.y) %>% 
        na.omit() %>% {paste("`", ., "`", collapse = ", ")}
    ) %>%
      mutate(
        values = ifelse(length(unique(na.omit(trial[[.y]]))) > 4,
                        paste(values, ", ..."),
                        values) 
      )
  ) %>%
  knitr::kable(caption = "Example data frame, `trial`") 
```

@@

```{r}
tibble::tribble(
  ~Argument,       ~Description,
  "`label`",       "specify the variable labels printed in table",
  "`type`",        "specify the variable type (e.g. continuous, categorical, etc.)",
  "`statistic`",   "change the summary statistics presented",
  "`digits`",      "number of digits the summary statistics will be rounded to",
  "`missing`",     "whether to display a row with the number of missing observations",
  "`missing_text`","text label for the missing number row",
  "`sort`",        "change the sorting of categorical levels by frequency",
  "`percent`",     "print column, row, or cell percentages"
) %>%
  knitr::kable(caption = "`tbl_summary()` function arguments") 
```

@@

```{r}
tibble::tribble(
  ~Function,             ~Description,
  "`add_p()`",           "add p-values to the output comparing values across groups",   
  "`add_overall()`",     "add a column with overall summary statistics",   
  "`add_n()`",           "add a column with N (or N missing) for each variable",
  "`add_difference()`",  "add column for difference between two group, confidemce interval, and p-value",
  "`add_stat_label()`",  "add label for the summary statistics shown in each row",   
  "`add_stat()`",        "generic function to add a column with user-defined values",
  "`add_q()`",           "add a column of q values to control for multiple comparisons"   
) %>%
  knitr::kable(caption = "`tbl_summary()` function arguments") 
```

>>>>

```{r}
trial %>%
  imap_dfr(
    ~tibble(
      colname = str_glue('`"{.y}"`'), 
      label = attr(.x, "label"), 
      class = class(.x), 
      values = trial %>% select(.y) %>% distinct() %>% 
        arrange(!!rlang::sym(.y)) %>% slice(1:4) %>% pull(.y) %>% 
        na.omit() %>% {paste("`", ., "`", collapse = ", ")}
    ) %>%
      mutate(
        values = ifelse(length(unique(na.omit(trial[[.y]]))) > 4,
                        paste(values, ", ..."),
                        values) 
      )
  ) %>%
  gt() %>%
  fmt_markdown(everything()) %>%
  cols_align("left", everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}Example data frame, \\texttt{trial}}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_trial_desc.tex")
```

@@

```{r}
tibble::tribble(
  ~Argument,       ~Description,
  "`label`",       "specify the variable labels printed in table",
  "`type`",        "specify the variable type (e.g. continuous, categorical, etc.)",
  "`statistic`",   "change the summary statistics presented",
  "`digits`",      "number of digits the summary statistics will be rounded to",
  "`missing`",     "whether to display a row with the number of missing observations",
  "`missing_text`","text label for the missing number row",
  "`sort`",        "change the sorting of categorical levels by frequency",
  "`percent`",     "print column, row, or cell percentages"
) %>%
  gt() %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl_summary()} function arguments}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_args.tex")

```

@@

```{r}
tibble::tribble(
  ~Function,             ~Description,
  "`add_p()`",           "add p-values to the output comparing values across groups",   
  "`add_overall()`",     "add a column with overall summary statistics",   
  "`add_n()`",           "add a column with N (or N missing) for each variable",
  "`add_difference()`",  "add column for difference between two group, confidemce interval, and p-value",
  "`add_stat_label()`",  "add label for the summary statistics shown in each row",   
  "`add_stat()`",        "generic function to add a column with user-defined values",
  "`add_q()`",           "add a column of q values to control for multiple comparisons"   
)%>%
  gt(caption = "`tbl_summary()` functions to add information") %>%
  fmt_markdown(everything()) %>%
  fmt_markdown(everything()) %>%
  as_latex() %>%
  as.character() %>%
  str_replace(fixed("\\toprule"), fixed("\\caption{\\label{tab:}\\texttt{tbl_summary()} functions to add information}\\\\\n\\toprule")) %>%
  readr::write_lines("tbl_tbl_summary_family.tex")
```

### 2020-12-09 tbl_trial_desc.tex
Update tbl_trial_desc.tex
in progress

\begin{table}

\caption{\label{tab:unnamed-chunk-1}Example data frame, `trial`}
\centering
\begin{tabular}[t]{l|l|l|l}
\hline
colname & label & class & values\\
\hline
trt & Chemotherapy Treatment & character & ` Drug A `, ` Drug B `\\
\hline
age & Age & numeric & ` 6 `, ` 9 `, ` 10 `, ` 17 ` , ...\\
\hline
marker & Marker Level (ng/mL) & numeric & ` 0.003 `, ` 0.005 `, ` 0.013 `, ` 0.015 ` , ...\\
\hline
stage & T Stage & factor & ` T1 `, ` T2 `, ` T3 `, ` T4 `\\
\hline
grade & Grade & factor & ` I `, ` II `, ` III `\\
\hline
response & Tumor Response & integer & ` 0 `, ` 1 `\\
\hline
death & Patient Died & integer & ` 0 `, ` 1 `\\
\hline
ttdeath & Months to Death/Censor & numeric & ` 3.53 `, ` 5.33 `, ` 6.32 `, ` 7.27 ` , ...\\
\hline
\end{tabular}
\end{table}

>>>>

\captionsetup[table]{labelformat=empty,skip=1pt}
\begin{longtable}{ll}
\caption{\label{tab:}tbl_summary() function arguments}\\
\toprule
Argument & Description \\ 
\midrule
\texttt{label} & specify the variable labels printed in table \\ 
\texttt{type} & specify the variable type (e.g. continuous, categorical, etc.) \\ 
\texttt{statistic} & change the summary statistics presented \\ 
\texttt{digits} & number of digits the summary statistics will be rounded to \\ 
\texttt{missing} & whether to display a row with the number of missing observations \\ 
\texttt{missing\_text} & text label for the missing number row \\ 
\texttt{sort} & change the sorting of categorical levels by frequency \\ 
\texttt{percent} & print column, row, or cell percentages \\ 
\bottomrule
\end{longtable}
